### 2019-08-31 reports/thesis/book.tex
Change github address

Parts of this thesis have been published by the author:
\begin{itemize}
  \item\nobibliography*\bibentry{lo2019detection}
\end{itemize}

@@

The uncertainty of the projection was modelled using a compound Poisson distribution. This arises from x-ray photon arrivals being a Poisson process and each photon has random energy. This resulted in a linear relationship between the mean and variance of the grey value in the projection. Fitting of the compound Poisson distribution using the expectation-maximisation algorithm was unsuccessful due to identifiability issues with the model. Instead, a gamma distributed generalised linear model was fitted and used for variance prediction and to quantify the uncertainty.

Software, called \emph{aRTist}, was used to simulate the projection and compared with the obtained projection. The comparison was done under the face of uncertainty by treating each pixel as a hypothesis test. To overcome the imperfections of the simulation, the empirical null filter was used to cater for the model misspecification so that sensible inference was achieved. Voids with diameters in the order of millimetres were detectable.

@@

Probability and statistics is used throughout in science to handle data and uncertainty. In particular, undergraduates are drilled to quote confidence intervals, use an appropriate number of significant figures and plot error bars in their studies. In physics, probability is used to model randomness in quantum mechanics and used to handle millions of particles in statistical mechanics. Uncertainty is a daily occurrence.

@@

The aim of this thesis is to investigate if it is possible to do quality control of additive manufactured products using only a few x-ray projections to speed up the quality control process. By using fewer x-ray projections, uncertainty is introduced. This is where statistics comes in. It enables the sensible handling of uncertainty from sources of errors such as from the random behaviour of x-ray photons or from the model misspecification of the problem.

@@

In Chapter \ref{chapter1}, x-ray computed tomography and additive manufacturing is reviewed. Sources of error were looked at and it was investigated to see how they were handled. In Chapter \ref{chapter2}, a test sample was additive manufactured and the chapter describes how experimental x-ray projections were obtained. Shading correction is explained here and it was used to remove sources of systematic errors in the projections. In Chapter \ref{chapter3}, the compound Poisson distribution is studied so that it can be used to model the detection of x-rays. In Chapter \ref{chapter4}, the uncertainty in the projection was quantified using the variance and generalised linear models were used to predict it. In Chapter \ref{chapter5}, statistical techniques were employed to look for defects in the test sample under the face of uncertainty. The empirical null filter was used to cater for any model misspecification so that sensible conclusions were made. The thesis ends with an evaluation in Chapter \ref{chapter6}.

Undergraduate level physics and statistics is assumed. The physics and mathematics used can be reviewed in undergraduate textbooks such as \cite{serway2018physics} and \cite{riley2006mathematical} respectively. The statistics can be reviewed in \cite{rice2009mathematical}. Knowledge of generalised linear models \citep{nelder1972generalized,nelder1972generalized_2, mccullagh1984generalized} and analysis of variance (ANOVA) is also assumed.

This thesis can be reproduced using the source code in the \emph{GitHub} repository \url{https://github.com/shermanip/oxwasp_phd}.

>>>>

Parts of this thesis is anticipated to be published by the author:
\begin{itemize}
  \item\nobibliography*\bibentry{lo2019detection}
\end{itemize}

@@

The uncertainty of the projection was modelled using a compound Poisson distribution. This arises from x-ray photon arrivals being a Poisson process and each photon has random energy. This resulted in a linear relationship between the mean and variance of the grey value in the projection. Fitting of the compound Poisson distribution using the expectation-maximisation algorithm was unsuccessful due to identifiability issues with the model. Instead, a gamma distributed generalised linear model was fitted and used for variance prediction to quantify the uncertainty.

Software, called \emph{aRTist}, was used to simulate the projection and compared with the obtained projection in the face of uncertainty by treating each pixel as a hypothesis test. To overcome the imperfections of the simulation, the empirical null filter was used to cater for model misspecification so that sensible inference was achieved. This was done by locally normalising the test statistics using the mode. Voids with diameters in the order of millimetres were detectable.

@@

@@

The main aim of this thesis is to investigate if it is possible to do quality control of additive manufactured products using only a few x-ray projections to speed up the quality control process. By using fewer x-ray projections, uncertainty is introduced. This is where statistics comes in. It enables the sensible handling of uncertainty from sources of error such as random error and systematic error.

The analysis was done by comparing the experimental projection with a simulated projection to look for areas with disagreement in the face of uncertainty. Random error can arise from how x-ray photons are produced in an x-ray tube and how they interact with the additive manufactured product and the x-ray detector. This was modelled by using the compound Poisson distribution. Incorrect simulation of the projection can cause systematic error and this was corrected using the empirical null filter. These sources of error were considered in the comparison of projections with the use of hypothesis testing.

@@

In Chapter \ref{chapter1}, x-ray computed tomography and additive manufacturing is reviewed. Sources of error were looked at and it was investigated to see how they were handled. In Chapter \ref{chapter2}, a test sample was additive manufactured and the chapter describes how experimental x-ray projections were obtained. Shading correction is explained here and it was used to remove sources of systematic errors in the projections. In Chapter \ref{chapter3}, the compound Poisson distribution is studied so that it can be used to model the detection of x-rays. In Chapter \ref{chapter4}, the uncertainty in the projection was quantified using the variance and generalised linear models were used to predict it. In Chapter \ref{chapter5}, novel statistical techniques were developed and implemented to look for defects in the test sample in the face of uncertainty. This was done by comparing the experimental projection with a simulated projection and looking for any disagreement. The empirical null filter was used to cater for any model misspecification so that sensible conclusions were made. The thesis ends with an evaluation in Chapter \ref{chapter6}.

The results presented in this thesis can be reproduced using the source code in the \emph{GitHub} repository \url{https://github.com/shermanlo77/oxwasp_phd}.

### 2019-08-31 reports/thesis/chapters/2_dataCollection.tex
Add scale bar

The objective of this thesis is to investigate if voids can be detected using a single projection. An experiment was conducted where a test sample was additively manufactured with purposely designed voids. This was done by comparing a projection of the test sample with the simulation of that projection as if the voids were not there. The simulated projections were produced by software called \emph{aRTist} \citep{bellon2007artist, jaenisch2008artist, bellon2012radiographic}. It can simulate projections of the test sample given the specifications of the CT apparatus, such as the x-ray source and the x-ray detector, and the CAD of the test sample \citep{bellon2011simulation, deresch2012simulating}.

@@

Greyscale projections were taken for calibration \citep{wang2008experimental} in addition to the projection of the test object. These are projections with nothing between the source and the detector with the x-ray tube at different powers. The power was varied by fixing the potential difference and varying the current. The greyscale projections were used for calibration such as shading correction. The greyscale projection with the x-ray turned off is called the black image. The greyscale projection with the x-ray set up the same when obtaining the test sample projection is called the white image.

>>>>

The objective of this thesis is to investigate if voids can be detected using a single projection. An experiment was conducted where a test sample was additively manufactured with purposely designed voids. This was done by comparing a projection of the test sample with the simulation of that projection as if the voids were not there. The simulated projections were produced by software called \emph{aRTist} \citep{bellon2007artist, jaenisch2008artist, bellon2012radiographic}.

@@

Greyscale projections were taken in addition to the projection of the test object. These are projections with nothing between the source and the detector with the x-ray tube at different powers. The power was varied by fixing the potential difference and varying the current. The greyscale projections were used for calibration such as shading correction. The greyscale projection with the x-ray turned off is called the black image. The greyscale projection with the x-ray set up the same when obtaining the test sample projection is called the white image.

### 2019-08-31 reports/thesis/chapters/3_compoundPoisson.tex

@@

In an x-ray tube, photons are emitted as a Poisson process \citep{cierniak2011x} and each photon has some random energy due to bremsstrahlung and characteristic radiation \citep{sun2012overview}. This shares similarities to the compound Poisson. Let $Y$ be the number of photons emitted for some time exposure $\tau$, then $Y\sim\poisson(\lambda)$. Each photon is assumed to be i.i.d.~with energy $U_i$ for $i=1,2,3,\dotsc$. $U_i$ has p.d.f.~$p_U(u)$. The random variables discussed here covers all the latent variables in the compound Poisson.

@@

It can be shown that the compound Poisson-gamma distribution is in the exponential family for fixed $\alpha$ \citep{jorgensen1987exponential}. To show this, it is useful to parametrise the compound Poisson-gamma distribution using the following:
\begin{equation}
  p=\frac{2+\alpha}{1+\alpha}
  \ ,
\end{equation}
\begin{equation}
  \mu=\frac{\lambda\alpha}{\beta}
  \ ,
\end{equation}
\begin{equation}
  \phi = \frac{\alpha+1}{\beta^{2-p}(\lambda\alpha)^{p-1}}
  \ .
\end{equation}
The parameters $p$, $\mu$ and $\phi$ are called the index, mean and dispersion parameters respectively. The parameters take the values of $1<p<2$, $\mu>0$ and $\phi>0$. After parametrising, it can be shown that the p.m.f.~at zero is
\begin{equation}
  \prob(X=0) = \exp
  \left[
      -\frac{\mu^{2-p}}{\phi(2-p)}
  \right]
\end{equation}
and the p.d.f.~for $x>0$ is
\begin{equation}
  p_X(x) = 
  \exp\left[
    \frac{1}{\phi}
    \left(
      x\frac{\mu^{1-p}}{1-p}-\frac{\mu^{2-p}}{2-p}
    \right)
  \right]
  \frac{1}{x}
  \sum_{y=1}^{\infty}W_y(x,p,\phi)
\end{equation}
where
\begin{equation}
  W_y = W_y(x,p,\phi)=\frac{x^{y\alpha}}{\phi^{y(1+\alpha)}(p-1)^{y\alpha}(2-p)^yy!\Gamma(y\alpha)}
  \ .
\end{equation}
The derivation is shown in Appendix \ref{chapter:appendix_tweedie}. This is in the form of a generalised linear model \citep{nelder1972generalized, nelder1972generalized_2, mccullagh1984generalized} for fixed $p$ and $\phi$ because the above is in the form of a distribution in the dispersive exponential family. This has applications in, for example, insurance claim data \citep{jorgensen1994fitting, smyth2002fitting}.

@@

The saddlepoint approximation \citep{daniels1954saddlepoint} gives an approximate solution to inverting the Laplace transformation of the m.g.f.~giving the p.d.f. Inverting the Fourier transformation of the characteristic function also gives the p.d.f.~using computational methods \citep{dunn2008evaluation}. The saddlepoint approximation will be studied here.

@@

There were a few technical problems with the histogram because the compound Poisson has probability mass at zero and probability density for positive numbers. To correctly represent the empirical distribution of a compound Poisson random variable, a bar chart was used to show the frequency of a zero and a histogram to show the frequency density of positive numbers. However, the Normal approximation and the saddlepoint approximation does not have support at zero. Therefore, to compare these approximate densities to the empirical distribution fairly, a histogram containing both zero and positive samples was used when appropriate.

The evaluation of the p.d.f.~using the saddlepoint approximate required a bit of caution to avoid over/underflow problems. Suppose realizations of $X$ were simulated $\left\{x_1,x_2,x_3,\dotsc,x_n\right\}$. The saddlepoint approximation was computed up to a constant using
\begin{equation}
  p_X(x) \propto
  \exp\left[
    -\frac{\alpha+2}{2(\alpha+1)}
    \ln(x)
    -x\beta
    +\left(
    \frac{x\beta}{\alpha}
    \right)^{\frac{\alpha}{\alpha+1}}\lambda^{\frac{1}{\alpha+1}}(\alpha+1) - k
  \right]
\end{equation}
for 500 equally spaced points from and including the minimum non-zero simulated value to the maximum simulated value. $k$ is some constant which was chosen to be
\begin{equation}
  k =
  \max_{i\in\left\{1,2,3,\dotsc,n\right\}}
  \left[
    -\frac{\alpha+2}{2(\alpha+1)}
    \ln(x_i)
    -x_i\beta
    +\left(
      \frac{x_i\beta}{\alpha}
    \right)^{\frac{\alpha}{\alpha+1}}\lambda^{\frac{1}{\alpha+1}}(\alpha+1)
  \right]
  \ .
\end{equation}
The density was then was normalised by numerically integrating it using the trapezium rule using the 500 evaluated points.

A Q-Q plot is a plot which compares the empirical quantiles with the theoretical quantiles. Let
\begin{equation}
  F_X(x) = \prob(X\leqslant x)
\end{equation}
and
\begin{equation}
  \widehat{F}_X(x) = \frac{1}{n}\cdot\text{max}
  \left[
    \left(\sum_{i=1}^n\mathbb{I}(x_i\leqslant x)\right)-0.5,0
  \right]
  \ ,
\end{equation}
then a Q-Q plot is a parametric plot which plots $\widehat{F}_X^{-1}(p)$ against $F_X^{-1}(p)$ for $p=\frac{0.5}{n},\frac{1.5}{n},\frac{2.5}{n},\dotsc,\frac{n-0.5}{n}$. If $F_X(x)$ and $\widehat{F}_X(x)$ are similar, a Q-Q plot should be a straight line with gradient 1, intercepting the origin. For the exact method and the saddlepoint approximate, $F_X(x)$ was found numerically by evaluating the p.d.f.~at $10\,000$ equally spaced points from and including the minimum to the maximum of the simulated samples, and then summing the required trapeziums. $\widehat{F}_X^{-1}(p)$ was then calculated by interpolation. Because the Normal and saddlepoint approximation does not support zero, the Q-Q plot was omitted for small $\lambda$.

@@

For low $\lambda$ (Figures \ref{fig:compoundPoisson_histogram_1_1_1}, \ref{fig:compoundPoisson_histogram_1_100_1} and \ref{fig:compoundPoisson_histogram_approx}) there is a chance of simulating zeros. For $\lambda = 1$, the Normal approximation failed to capture the probability mass at zero because the Normal distribution is symmetric and support negative values. The saddlepoint approximation did capture the probability mass at zero as shown by an increase in probability density towards zero. For $\CPoisson(1,100,1)$ in Figure \ref{fig:compoundPoisson_histogram_approx}, the compound Poisson-gamma p.d.f.~contains multiple peaks and the saddlepoint approximation was not flexible enough to capture them. In Figure \ref{fig:compoundPoisson_histogram_1_100_1}, the Q-Q plot for the exact method was quite sensitive at the tails of each peak, perhaps there were a few inaccuracies in the exact evaluation of the p.d.f.~or in the calculation or inversion of the c.d.f.

@@

\begin{figure}
  \centering
    \centerline{
    \begin{subfigure}[b]{\subSize}
        \includegraphics[width=\textwidth]{../figures/compoundpoisson/cpHistogram_CompoundPoissonNormlambda1alpha1beta1.eps}
        \caption{$\CPoisson(1,1,1)$ Normal approx.}
    \end{subfigure}
    \begin{subfigure}[b]{\subSize}
        \includegraphics[width=\textwidth]{../figures/compoundpoisson/cpHistogram_CompoundPoissonSaddlelambda1alpha1beta1.eps}
        \caption{$\CPoisson(1,1,1)$ saddlepoint approx.}
    \end{subfigure}
    }
    \vspace{1em}
    \centerline{
    \begin{subfigure}[b]{\subSize}
        \includegraphics[width=\textwidth]{../figures/compoundpoisson/cpHistogram_CompoundPoissonNormlambda1alpha100beta1.eps}
        \caption{$\CPoisson(1,100,1)$ Normal approx.}
    \end{subfigure}
    \begin{subfigure}[b]{\subSize}
        \includegraphics[width=\textwidth]{../figures/compoundpoisson/cpHistogram_CompoundPoissonSaddlelambda1alpha100beta1.eps}
        \caption{$\CPoisson(1,100,1)$ saddlepoint approx.}
        \label{fig:compoundPoisson_histogram_approx_1_100_1}
    \end{subfigure}
    }
    \caption{1\,000 $\CPoisson(1,\alpha,1)$ random variables were simulated and its empirical distribution is compared to the p.d.f.~evaluated using approximate methods. The dotted red line shows the 68\% confidence interval of the expected frequency density.}
    \label{fig:compoundPoisson_histogram_approx}
\end{figure}

@@

The graphical model in Figure \ref{fig:compoundPoisson_graphicalModel} illustrates how all of these variables link together. $a$ and $\kappa$ are unknown parameters but can be estimated beforehand from replicate black images. The energy of each photon $U\sim\gammaDist(\alpha,\beta)$ was omitted in the graphical model because the conditional distribution $X|Y\sim\gammaDist(Y\alpha,\beta)$ encapsulates each detected photon energy already.

@@

The EM algorithm \citep{dempster1977maximum} is proposed as a method to estimate the parameters of a $X\sim\CPoisson(\lambda,\alpha,\beta)$ random variable given a sample of measurements of it $\left\{x_1,x_2,x_3,\dotsc,x_n\right\}$. The use of the EM algorithm here for the compound Poisson is similar to \cite{elbakri2003statistical, xu2009electronic}.

>>>>

The compound Poisson has applications in, for example, modelling rainfall \citep{revfeim1984initial} and insurance claims \citep{jorgensen1994fitting, smyth2002fitting}.

@@

In an x-ray tube, photons are emitted as a Poisson process \citep{whiting2006properties, cierniak2011x} and each photon has some random energy due to bremsstrahlung and characteristic radiation \citep{sun2012overview}. This shares similarities to the compound Poisson. Let $Y$ be the number of photons emitted for some time exposure $\tau$, then $Y\sim\poisson(\lambda)$. Each photon is assumed to be i.i.d.~with energy $U_i$ for $i=1,2,3,\dotsc$. $U_i$ has p.d.f.~$p_U(u)$. The random variables discussed here covers all the latent variables in the compound Poisson.

@@

It can be shown that the compound Poisson-gamma distribution is in the exponential family for fixed $\alpha$ \citep{jorgensen1987exponential}. To show this, it is useful to parametrise the compound Poisson-gamma distribution using the following:
\begin{equation}
  p=\frac{2+\alpha}{1+\alpha}
  \ ,
\end{equation}
\begin{equation}
  \mu=\frac{\lambda\alpha}{\beta}
  \ ,
\end{equation}
\begin{equation}
  \phi = \frac{\alpha+1}{\beta^{2-p}(\lambda\alpha)^{p-1}}
  \ .
\end{equation}
The parameters $p$, $\mu$ and $\phi$ are called the index, mean and dispersion parameters respectively. The parameters take the values of $1<p<2$, $\mu>0$ and $\phi>0$. After parametrising, it can be shown that the p.m.f.~at zero is
\begin{equation}
  \prob(X=0) = \exp
  \left[
      -\frac{\mu^{2-p}}{\phi(2-p)}
  \right]
\end{equation}
and the p.d.f.~for $x>0$ is
\begin{equation}
  p_X(x) = 
  \exp\left[
    \frac{1}{\phi}
    \left(
      x\frac{\mu^{1-p}}{1-p}-\frac{\mu^{2-p}}{2-p}
    \right)
  \right]
  \frac{1}{x}
  \sum_{y=1}^{\infty}W_y(x,p,\phi)
\end{equation}
where
\begin{equation}
  W_y = W_y(x,p,\phi)=\frac{x^{y\alpha}}{\phi^{y(1+\alpha)}(p-1)^{y\alpha}(2-p)^yy!\Gamma(y\alpha)}
  \ .
\end{equation}
The derivation is shown in Appendix \ref{chapter:appendix_tweedie}. This is in the form of a generalised linear model \citep{nelder1972generalized, nelder1972generalized_2, mccullagh1984generalized} for fixed $p$ and $\phi$ because the above is in the form of a distribution in the dispersive exponential family.

@@

The saddlepoint approximation \citep{daniels1954saddlepoint} gives an approximate solution to inverting the Laplace transformation or the m.g.f.~giving the p.d.f.~and has been used in XCT \citep{elbakri2003statistical, elbakri2003efficient}. Inverting the Fourier transformation of the characteristic function also gives the p.d.f.~using computational methods \citep{dunn2008evaluation}. The saddlepoint approximation will be studied here.

@@

There were a few technical problems with the histogram because the compound Poisson has probability mass at zero and probability density for positive numbers. To correctly represent the empirical distribution of a compound Poisson random variable, a bar chart was used to show the frequency of a zero and a histogram to show the frequency density of positive numbers. However, the Normal approximation and the saddlepoint approximation does not have mass support at zero. Therefore, to compare these approximate densities to the empirical distribution fairly, a histogram containing both zero and positive samples was used when appropriate.

The evaluation of the p.d.f.~using the saddlepoint approximate required a bit of caution to avoid over/underflow problems. Suppose realizations of $X$ were simulated $\left\{x_1,x_2,x_3,\dotsc,x_n\right\}$. The saddlepoint approximation was computed up to a constant using
\begin{equation}
  p_X(x) \propto
  \exp\left[
    -\frac{\alpha+2}{2(\alpha+1)}
    \ln(x)
    -x\beta
    +\left(
    \frac{x\beta}{\alpha}
    \right)^{\frac{\alpha}{\alpha+1}}\lambda^{\frac{1}{\alpha+1}}(\alpha+1) - k
  \right]
\end{equation}
for 10\,000 equally spaced points from and including the minimum non-zero simulated value to the maximum simulated value. $k$ is some constant which was chosen to be
\begin{equation}
  k =
  \max_{i\in\left\{1,2,3,\dotsc,n\right\}}
  \left[
    -\frac{\alpha+2}{2(\alpha+1)}
    \ln(x_i)
    -x_i\beta
    +\left(
      \frac{x_i\beta}{\alpha}
    \right)^{\frac{\alpha}{\alpha+1}}\lambda^{\frac{1}{\alpha+1}}(\alpha+1)
  \right]
  \ .
\end{equation}
The density was then was normalised by numerically integrating it using the trapezium rule using the 10\,000 evaluated points.

A Q-Q plot is a plot which compares the empirical quantiles with the theoretical quantiles. Let
\begin{equation}
  F_X(x) = \prob(X\leqslant x)
\end{equation}
and
\begin{equation}
  \widehat{F}_X(x) = \frac{1}{n}\cdot\text{max}
  \left[
    \left(\sum_{i=1}^n\mathbb{I}(x_i\leqslant x)\right)-0.5,0
  \right]
  \ ,
\end{equation}
then a Q-Q plot is a parametric plot which plots $\widehat{F}_X^{-1}(p)$ against $F_X^{-1}(p)$ for $p=\frac{0.5}{n},\frac{1.5}{n},\frac{2.5}{n},\dotsc,\frac{n-0.5}{n}$. If $F_X(x)$ and $\widehat{F}_X(x)$ are similar, a Q-Q plot should be a straight line with gradient 1, intercepting the origin. For the exact method and the saddlepoint approximation, $F_X(x)$ was found numerically by evaluating the p.d.f.~at $10\,000$ equally spaced points from and including the minimum to the maximum of the simulated samples, and then summing the required trapeziums. Because the saddlepoint approximation does not support zero, the numerical integration cannot start at zero. $\widehat{F}_X^{-1}(p)$ was then calculated by interpolation.

@@

For low $\lambda$ (Figures \ref{fig:compoundPoisson_histogram_1_1_1}to \ref{fig:compoundPoisson_histogram_approx_1_100_1}) there is a chance of simulating zeros. For $\lambda = 1$, the Normal approximation failed to capture the probability mass at zero because the Normal distribution is symmetric and support negative values. The saddlepoint approximation did capture the probability mass at zero as shown by an increase in probability density towards zero. For $\CPoisson(1,100,1)$ in Figure \ref{fig:compoundPoisson_histogram_approx_1_100_1}, the compound Poisson-gamma p.d.f.~contains multiple peaks and the saddlepoint approximation was not flexible enough to capture them. In Figure \ref{fig:compoundPoisson_histogram_1_100_1}, the Q-Q plot for the exact method was quite sensitive at the tails of each peak, perhaps there were a few inaccuracies in the exact evaluation of the p.d.f.~or in the calculation of the numerical calculation of the c.d.f.~and its inversion.

@@

\begin{figure}
  \centering
    \centerline{
    \begin{subfigure}[b]{\subSize}
        \includegraphics[width=\textwidth]{../figures/compoundpoisson/cpHistogram_CompoundPoissonNormlambda1alpha1beta1.eps}
        \caption{Histogram - Normal approx.}
    \end{subfigure}
    \begin{subfigure}[b]{\subSize}
        \includegraphics[width=\textwidth]{../figures/compoundpoisson/cpHistogram_qq_CompoundPoissonNormlambda1alpha1beta1.eps}
        \caption{Q-Q plot - Normal approx.}
    \end{subfigure}
    }
    \vspace{1em}
    \centerline{
    \begin{subfigure}[b]{\subSize}
        \includegraphics[width=\textwidth]{../figures/compoundpoisson/cpHistogram_CompoundPoissonSaddlelambda1alpha1beta1.eps}
        \caption{Histogram - Saddlepoint approx.}
    \end{subfigure}
    \begin{subfigure}[b]{\subSize}
        \includegraphics[width=\textwidth]{../figures/compoundpoisson/cpHistogram_qq_CompoundPoissonSaddlelambda1alpha1beta1.eps}
        \caption{Q-Q plot - Saddlepoint approx.}
    \end{subfigure}
    }
    \caption{1\,000 $\CPoisson(1,1,1)$ random variables were simulated and its empirical distribution is compared to the approximate p.d.f. On the left, the dotted red line shows the 68\% confidence interval of the expected frequency density.}
    \label{fig:compoundPoisson_histogram_approx_1_1_1}
\end{figure}

\begin{figure}
  \centering
    \centerline{
    \begin{subfigure}[b]{\subSize}
        \includegraphics[width=\textwidth]{../figures/compoundpoisson/cpHistogram_CompoundPoissonNormlambda1alpha100beta1.eps}
        \caption{Histogram - Normal approx.}
    \end{subfigure}
    \begin{subfigure}[b]{\subSize}
        \includegraphics[width=\textwidth]{../figures/compoundpoisson/cpHistogram_qq_CompoundPoissonNormlambda1alpha100beta1.eps}
        \caption{Q-Q plot - Normal approx.}
    \end{subfigure}
    }
    \vspace{1em}
    \centerline{
    \begin{subfigure}[b]{\subSize}
        \includegraphics[width=\textwidth]{../figures/compoundpoisson/cpHistogram_CompoundPoissonSaddlelambda1alpha100beta1.eps}
        \caption{Histogram - Saddlepoint approx.}
    \end{subfigure}
    \begin{subfigure}[b]{\subSize}
        \includegraphics[width=\textwidth]{../figures/compoundpoisson/cpHistogram_qq_CompoundPoissonSaddlelambda1alpha100beta1.eps}
        \caption{Q-Q plot - Saddlepoint approx.}
    \end{subfigure}
    }
    \caption{1\,000 $\CPoisson(1,100,1)$ random variables were simulated and its empirical distribution is compared to the approximate p.d.f. On the left, the dotted red line shows the 68\% confidence interval of the expected frequency density.}
    \label{fig:compoundPoisson_histogram_approx_1_100_1}
\end{figure}

@@

The graphical model in Figure \ref{fig:compoundPoisson_graphicalModel} illustrates how all of these variables link together. $a$ and $\kappa$ are unknown parameters but can be estimated beforehand from replicate black images. Care must be taken to use the replicate black images for either shading correction or for estimating $a$ and $\kappa$ to avoid using the data twice. The energy of each photon $U\sim\gammaDist(\alpha,\beta)$ was omitted in the graphical model because the conditional distribution $X|Y\sim\gammaDist(Y\alpha,\beta)$ encapsulates each detected photon energy already.

@@

The EM algorithm \citep{dempster1977maximum} is proposed as a method to estimate the parameters of a $X\sim\CPoisson(\lambda,\alpha,\beta)$ random variable given a sample of measurements of it $\left\{x_1,x_2,x_3,\dotsc,x_n\right\}$. The use of the EM algorithm for the compound Poisson in XCT has been studied in \cite{elbakri2003statistical, xie2008x, xu2009electronic}.
